Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex
update experiments
minor

The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}. Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

@@

To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to 539, while CVC4 and Z3-str3 got almost the same number of timeouts with the results of timeout set to 10s. Z3 also managed to reduce the number of timeouts to 821. If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.

>>>>

The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}. Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
\multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

@@

We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3-str3 got almost the same number of failed cases. Z3 also managed to reduce the number of failed cases to 821. %If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.
